---
title: "Covid-19-Virus-Trends"
author: "NJI JOSHUA"
date: "30/07/2020"
output: html_document
---

In this project am investigating Which countries have had the highest number of Covid-19 positive cases against the number of tests

# Understanding our data

Loading the readr library

```{r}
library(readr)
```

Loading the file containing our dataset

```{r}
covid_df <- read.csv('covid19.csv')
```

Displaying the dimention of our data

```{r}
dim(covid_df)
```

Displaying the column names

```{r}
vector_cols <- colnames(covid_df)
print(vector_cols)
```

Displaying part of our dataset

```{r}
head(covid_df)
```

Loading the tibble library and Displaying the summary of our dataset

```{r}
library(tibble)
glimpse(covid_df)
```

Ans: The glimpse fuction give use a summary of the dataset so that we have a clue of the data we are working with

# Isolating the rows we need from our dataset

Filtering only rows related to All States

```{r}
library(dplyr)
covid_df_all_states <- covid_df %>%
  filter(Province_State == "All States") %>%
  select(-Province_State)
covid_df_all_states
```

Ans: We can remove the Province state column without losing information since we have already filtered the all the data belonging to All States.

# Isolating the Columns We Need from out dataset 

Selecting data belonging to daily measures

```{r}
covid_df_all_states_daily <- covid_df_all_states %>%
  select(Date, Country_Region, active, hospitalizedCurr, daily_tested, daily_positive)

covid_df_all_states_daily
```

# Extracting the Top Ten Tested Cases Countries

Grouping and summarising our data frame

```{r}
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>%
  group_by(Country_Region)%>%
  summarise( tested = sum(daily_tested), positive = sum(daily_positive), active = sum(active), hospitalized = sum(hospitalizedCurr))%>%
  arrange(desc(tested))
covid_df_all_states_daily_sum
```

Extracting the top ten rows

```{r}
covid_top_10 <- head(covid_df_all_states_daily_sum, 10)
```


#Identifying the Highest Positive Against Tested Cases

Creating vectors from our dataframe
```{r}
countries <- c(covid_top_10$Country_Region)
tested_cases <- c(covid_top_10$tested)
positive_cases <- c(covid_top_10$positive)
active_cases <- c(covid_top_10$active)
hospitalized_cases <- c(covid_top_10$hospitalized)
```

Naming the vectors

```{r}
names(positive_cases) <- countries
names(tested_cases) <- countries
names(active_cases) <- countries
names(hospitalized_cases) <- countries
```


```{r}
positive_cases/ tested_cases

```

```{r}
ositive_tested_top_3 <- c("United Kingdom" = 0.11, "United States" = 0.10, "Turkey" = 0.08)
```

#Keeping relevant information

Creating vectors

```{r}
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)
united_states <- c(0.10, 17282363, 1877179, 0, 0)
turkey <- c(0.08, 2031192, 163941, 2980960, 0)
```

Creating a matrix containing the vectors created above

```{r}
covid_mat <- rbind(united_kingdom,united_states,turkey)
```

Renaming the matrix columns

```{r}
colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")
covid_mat
```



#Putting all together 

Creating and asigning our question and answer variable

```{r}
question <- "Which countries have had the highest number of positive cases against the number of tests?"
answer <- c("Positive tested cases" = positive_tested_top_3)
```

Creating our lise

```{r}
dataframes_list <- list(complete = covid_df, all_states = covid_df_all_states, daily = covid_df_all_states_daily,top_10 = covid_top_10)
matrices_list <- list(covid_mat)
vectors_list <- list(vector_cols, countries)

data_structure_list <- list("dataframe" = dataframes_list, "matrix" = matrices_list, "vector" = vectors_list)

covid_analysis_list <- list(question, answer, data_structure_list)
covid_analysis_list[2]
```

From our result we see that the to 3 countries in terms of positive cases againt number of test are United Kindom, United State and Turkey. This was gotten by dividing out positive case by number tested after we had cleaned our data set.